### 2020-02-02 article.tex
some problems fixed

@@

A neural network with arbitrary depth and non-linearities, with dropout applied before every weight layer, is mathematically equivalent to an approximation to the probabilistic deep Gaussian process \cite{Gal2016}.

@@

Let $W_i$ be a random matrix of dimensions $K \times K_{i-1}$ for each layer $i$, and write
$\omega = \{ W_i \}^L_{i=1}$. A priori,we let each row of $W_i$ distribute according to the $p(W)$ above. In addition, assume vectors $m_i$ of dimensions $K_i$ for each GP layer. The predictive probability of the deep GP model given some precision parameter $\tau > 0$ can be parameterized as Equation \eqref{eq:gpPriority}.

@@

\subsection{Proposed method}
\label{section:proposedMethod}
As mentioned before, our experiment aims to find out if fMRI scans carry any hidden information without taking time-based sequences in action. Accordingly, we examined some previous researches in this field and an eye-catching example of this glance is Sarraf and Tofighi's adopted LeNet-5 architecture \cite{Sarraf2016}. Their algorithm concatenates fMRI images based on $z$ and $t$ axis and does not make any assumptions about the disease or the data (except their unknown patient selection criteria), making it a potential applicable solution to different disease diagnosis tasks. In brief, each patient's scan is presented as a huge two-dimensional matrix which is then fed to a CNN network. Although this method has shown huge success in the case of Alzheimer's (based on large ADNI dataset), our experiments clarify that it is not suitable for Parkinson's disease diagnosis with a small dataset (such as OpenfMRI ds000245). In addition to that, Sarraf and Tofighi's method consumes a huge amount of memory and demands a powerful processor due to its large dimensions of data.

Without a doubt, fMRI scans are nothing but spatial and temporal connectivities. As we aim to focus on spatial relations and put temporal ones aside, our algorithm must try to keep all of that information in calculations. Besides, Sarraf and Tofighi's method loses a lot of these connectivities by flattening data toward the $z$ axis. In addition to that, the mentioned data conversion will increase our model complexity and variance, especially in a case like Parkinson's disease dataset. In fact, by resizing 198 slices of $39 \times 64 \times 64$ voxels to a 2D $2496 \times 12672$ pixels, we are adding a lot of unnecessarily and incorrect spatial connectivities based on the $t$ axis and losing some important ones in the $z$ axis by misplacing them. As a result, it is predictable that flattening algorithm may lead to overfitting and compute-intensive calculations which can be seen in Figure \ref{fig:SarrafParkinsonTestResult}. This experiment ran on an NVIDIA\textsuperscript{\tiny\textregistered} GTX1080 and took $6h \; 47m \; 36s$.

@@

\section{Experiments and results}
\label{section:results}
As discussed in Section \ref{section:proposedMethod}, our method does not demand high processing power so we can use a CPU for our experiments. All of the tests had been run on an Intel\textsuperscript{\tiny\textregistered} 4710HQ CPU. Averagely, the training phase takes $1h \; 12m \; 4s$ and the test phase finishes in $6m \; 41s$. Also it worth mentioning that the application consumes 270 megabytes of RAM thanks to the TFRECORD file format.

@@

Figures \ref{fig:tests_1} to \ref{fig:tests_8} show different diagrams of loss and accuracy compared to normal CNNs. This behavior is the result of using dropouts which prevent gradient descent to smoothly decrease loss \cite{Gal2016}. These smooth steps can be seen in small parts of the diagram but not in the whole diagram. As we add dropout layers, gradient descent tries to minimize the loss of the training. As long as the dropout layers stay the same, everything works as expected. However, as the dropout layers vary, the loss changes dramatically and as a result, the loss diagram becomes noisy.

>>>>

\usepackage{hyperref}

@@

A neural network with arbitrary depth and non-linearities, with dropout applied before every weight layer, is mathematically equivalent to an approximation to the probabilistic deep Gaussian process (GP) \cite{Gal2016}.

@@

Let $W_i$ be a random matrix of dimensions $K_i \times K_{i-1}$ for each layer $i$, and write
$\omega = \{ W_i \}^L_{i=1}$. A priori,we let each row of $W_i$ distribute according to the $p(W)$ above. In addition, assume vectors $m_i$ of dimensions $K_i$ for each GP layer. The predictive probability of the deep GP model given some precision parameter $\tau > 0$ can be parameterized as Equation \eqref{eq:gpPriority}.

@@

\subsection{Proposed method}
\label{section:proposedMethod}
As mentioned before, our experiment aims to find out if fMRI scans carry any hidden information without taking time-based sequences in action. Accordingly, we examined some previous researches in this field and an eye-catching example of this glance is Sarraf and Tofighi's adopted LeNet-5 architecture \cite{Sarraf2016}. Their algorithm concatenates fMRI images based on depth ($z$) and time ($t$) axis and does not make any assumptions about the disease or the data (except their unknown patient selection criteria), making it a potential applicable solution to different disease diagnosis tasks. In brief, each patient's scan is presented as a huge two-dimensional matrix which is then fed to a CNN network. Although this method has shown huge success in the case of Alzheimer's (based on large ADNI dataset), our experiments clarify that it is not suitable for Parkinson's disease diagnosis with a small dataset (such as OpenfMRI ds000245). In addition to that, Sarraf and Tofighi's method consumes a huge amount of memory and demands a powerful processor due to its large dimensions of data.

Without a doubt, fMRI scans are nothing but spatial and temporal connectivities. As we aim to focus on spatial relations and put temporal ones aside, our algorithm must try to keep all of that information in calculations. Besides, Sarraf and Tofighi's method loses a lot of these connectivities by flattening data toward the $z$ axis. In addition to that, the mentioned data conversion will increase the model complexity and variance, especially in a case like Parkinson's disease dataset. In fact, by resizing 198 slices of $39 \times 64 \times 64$ voxels to a 2D $2496 \times 12672$ pixels, we are adding a lot of unnecessarily and incorrect spatial connectivities based on the $t$ axis and losing some important ones in the $z$ axis by misplacing them. As a result, it is predictable that flattening algorithm may lead to overfitting and compute-intensive calculations which can be seen in Figure \ref{fig:SarrafParkinsonTestResult}. This experiment ran on an NVIDIA\textsuperscript{\tiny\textregistered} GTX1080 and took $6h \; 47m \; 36s$.

@@

\section{Experiments and results}
\label{section:results}
As discussed in Section \ref{section:proposedMethod}, our method does not demand high processing power so we can use a CPU for our experiments. All of the tests had been run on an Intel\textsuperscript{\tiny\textregistered} 4710HQ CPU. Averagely, the training phase takes $1h \; 12m \; 4s$ and the test phase finishes in $6m \; 41s$. As described in Section \ref{section:data}, Parkinson's disease dataset consists of 30 samples of 198 time-slices containing \texttt{$39 \times 64 \times 64$} {\tiny $=(159,744)$} voxels. Also it worth mentioning that the application consumes 270 megabytes of RAM thanks to the TFRECORD file format. Implementation of the proposed method in Python using TensorFlow\textsuperscript{\tiny\textregistered} can we found on \href{https://github.com/amin-amini/BayseanFmriDiseaseDiagnosis}{this Github repository} \cite{SourceCode}.

@@

As we can see, the overall shape of the diagrams (loss and accuracy) in Figures \ref{fig:tests_1} to \ref{fig:tests_8} are extremely different than normal CNNs, as can bee seen in Figure \ref{fig:SarrafParkinsonTestResult}. This behavior is the result of using dropouts which prevent gradient descent to smoothly decrease loss \cite{Gal2016}. These smooth steps can be seen in small parts of the diagram but not in the whole diagram. As we add dropout layers, gradient descent tries to minimize the loss of the training. As long as the dropout layers stay the same, everything works as expected. However, as the dropout layers vary, the loss changes dramatically and as a result, the loss diagram becomes noisy.
